Computational methods in landscape ecology

### 2024-09-20 Manuscript.qmd
Remove numbering

format:
  pdf:
    keep-tex: true
    template-partials:
      - title.tex
    include-in-header:
      text: |
        \usepackage{lineno}\linenumbers
        \usepackage[noblocks]{authblk}
        \usepackage{setspace}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}

papersize: a4paper
fontsize: 10pt
geometry: margin=25mm
indent: 2m
linestretch: 1.5
number-sections: true

@@

# Abstract {.unnumbered}

## Purpose of Review {.unnumbered}

@@

## Recent findings {.unnumbered}

@@

## Summary {.unnumbered}

@@

# Acknowledgments {.unnumbered}

@@

## Funding {.unnumbered}

@@

## Author contributions {.unnumbered}

@@

## Conflict of Interest {.unnumbered}

@@

## Human and Animal Rights and Informed Consent {.unnumbered}

@@

# References {.unnumbered}

>>>>

format:
  pdf:
    keep-tex: true
    template-partials:
      - title.tex
    include-in-header:
      text: |
        \usepackage{lineno}\linenumbers
        \usepackage[noblocks]{authblk}
        \usepackage{setspace}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
papersize: a4paper
fontsize: 10pt
geometry: margin=25mm
indent: 2m
linestretch: 1.5
number-sections: false

@@

# Abstract

## Purpose of Review

@@

## Recent findings

@@

## Summary

@@

# Acknowledgments

@@

## Funding

@@

## Author contributions

@@

## Conflict of Interest

@@

## Human and Animal Rights and Informed Consent

@@

# References
